Efficient Handling of String-Number Conversion

### 2019-11-23 draft.tex
fix of ex 5.2

\begin{example}
If we consider the PFA ${\pa_x}=(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and let $Y{=}(v_1,v_2,\#v_1,\#v_2)$, we have\\
$\encode {\pa_x}( ``aaa" ) =\{ (Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3), Y{\rightarrow}(\semof{\epsilon},\semof{a},3,3)  \}$ and
$\decode {\pa_x}((Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3))=\{``aaa"\} $.
\end{example}

>>>>

\begin{example}
Let use consider the PFA ${\pa_x}=(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and let $Y{=}(v_1,v_2,\#v_1,\#v_2)$. Then we have\\
$\encode {\pa_x}( ``aaa" ) =\{ (Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3), Y{\rightarrow}(\semof{\epsilon},\semof{a},3,3)  \}$ and
$\decode {\pa_x}((Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3))=\{``aaa"\} $.
\footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ denote the function $\{x_1 \rightarrow n_1,\ldots, x_k\rightarrow n_k\}$.}
\end{example}
